Bibliography management: \texttt{biblatex} package

### 2023-09-16 resources/tools/tools.tex

\begin{tabularx}{\textwidth}{c|c|l}
  \hline \textbf{Język programowania} & \textbf{Biblioteki}      & \textbf{Nazwa podprojektu} \\ \hline
   Python                             & NumPy                    & cssfinder\_backend\_numpy \\
   Python                             & NumPy, Cython            & cssfinder\_backend\_numpy \\
   Python                             & NumPy, Numba             & cssfinder\_backend\_numpy \\
   Rust                               & Ndarray                  & cssfinder\_backend\_rust \\
   Rust                               & Ndarray, OpenBLAS        & cssfinder\_backend\_rust \\ \hline
\end{tabularx}

>>>>

\begin{tabularx}{\textwidth}{l|l|l}
  \hline \textbf{Język programowania} & \hspace{1.5cm} \textbf{Biblioteki}                    & \hspace{1cm} \textbf{Nazwa podprojektu}              \\ \hline
  \hspace{0.5cm} Python               & \hspace{0.5cm} NumPy                   \hspace{0.5cm} & \hspace{0.7cm} cssfinder\_backend\_numpy  \\
  \hspace{0.5cm} Python               & \hspace{0.5cm} NumPy, Cython           \hspace{0.5cm} & \hspace{0.7cm} cssfinder\_backend\_numpy  \\
  \hspace{0.5cm} Python               & \hspace{0.5cm} NumPy, Numba            \hspace{0.5cm} & \hspace{0.7cm} cssfinder\_backend\_numpy  \\
  \hspace{0.5cm} Rust                 & \hspace{0.5cm} Ndarray                 \hspace{0.5cm} & \hspace{0.7cm} cssfinder\_backend\_rust   \\
  \hspace{0.5cm} Rust                 & \hspace{0.5cm} Ndarray, OpenBLAS       \hspace{0.5cm} & \hspace{0.7cm} cssfinder\_backend\_rust   \\ \hline
\end{tabularx}
